%DO NOT MESS AROUND WITH THE CODE ON THIS PAGE UNLESS YOU %REALLY KNOW WHAT YOU ARE DOING
\begin{center}
\begin{huge}
\bfseries{Abstract}
\end{huge}
\end{center}
\noindent In recent times, there have been a lot of advancements in remotely controlled aerial vehicles technology. With the applications of Unmanned Aerial Vehicles or UAVs ranging from aerial photography to last-mile delivery options, they are becoming popular with the public. Lately, they have been used for activities such as illegal surveillance and terrorism. With an ever-increasing threat of unauthorized UAVs being deployed in high-security regions, consistent efforts have been made by the authorities to set up regulations on UAVs. But regulations are rarely enough to keep such activities in check.

\noindent The solution would be to create a system that can easily be deployed on a large scale to ward off unauthorised activities. Modern-day UAV detection systems either use RADAR, acoustic or visual identification technology to detect UAVs. But these systems are usually very convoluted, way too expensive or ginormous to be able to deploy in mass.

\noindent To counter these issues, we have developed a system that makes use of radio frequency signature detection methods to observe and possibly shut down such illegal activities. This involves the use of SDR for capturing RF signals and machine learning for the classification of the captured signals. The output of such a system can be used to then jam only the UAV signal without interfering with other signals. Subsequently, this system can also be integrated into an automatic anti-UAV system that can either disable or even take control of the UAVs.\pagebreak




