%DO NOT MESS AROUND WITH THE CODE ON THIS PAGE UNLESS YOU %REALLY KNOW WHAT YOU ARE DOING
\begin{thebibliography}{15}
\bibitem{1} D. Mototolea and C. Stolk, "Software Defined Radio for Analyzing Drone Communication Protocols," 2018 International Conference on Communications (COMM), 2018, pp. 485-490, doi: 10.1109/ICComm.2018.8484821.
\bibitem{2} Drone ecosystem policy Roadmap - Digital Sky Platform ,Ministry of Civil Aviation Government of India https://aviation.report/whitepapers/drone-ecosystem-policy-roadmap-book
% \bibitem{3} -Ji Wei Lin, "UAV monitoring techniques", The State Radio monitoring Centre of China,Beijing Monitoring Station, https://www.scribd.com/document/475429742/Day3-1000-1100-Civil-UAV-monitoring-techniques-JiWeilin-pdf

\bibitem{4} Lichtman, M., 2021. PySDR: A Guide to SDR and DSP using Python — PySDR: A Guide to SDR and DSP using Python 0.1 documentation. [online] Pysdr.org. Available at: <https://pysdr.org/> [Accessed 6 March 2021].
\bibitem{5} Aniket Mahanti, Niklas Carlsson, Carey Williamson, Martin Arlitt. Ambient Interference Effects in Wi-Fi Networks. 9th International IFIP TC 6 Networking Conference (NETWORKING), May 2010, Chennai, India. pp.160-173, ⟨10.1007/978-3-642-12963-6\_13⟩. ⟨hal-01056315⟩
\bibitem{6}M. Ezuma, F. Erden, C. Kumar Anjinappa, O. Ozdemir and I. Guvenc, "Detection and Classification of UAVs Using RF Fingerprints in the Presence of Wi-Fi and Bluetooth Interference," in IEEE Open Journal of the Communications Society, vol. 1, pp. 60-76, 2020, doi: 10.1109/OJCOMS.2019.2955889.
\end{thebibliography}
